
%
\documentclass[a4paper,oneside,11pt]{book}

%%%%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}           
\usepackage{mathabx}           %\usepackage{bbm}

\usepackage{textcomp}
\usepackage{lmodern}
\usepackage[a4paper,margin=2cm]{geometry} 

\usepackage{hyperref}     

\usepackage[english,frenchb]{babel}
\usepackage{listingsutf8}   % 

\makeindex

\begin{document} 

\bibliographystyle{unsrtnat} 
\corrPosition{1}

%%
\selectlanguage{frenchb}

%
    This is the file number 2. It contains an equation that should not kill your computer.

By the way, the last line of this file is the ``end equation''.

\begin{equation}
    f(x)=\frac{ x }{ 0 }.
\end{equation}
  

\tableofcontents

\chapter{First chapter}
This is the first file which includes the number 5

This is the file number 5.      %
File number 5 done. 

Here are two input on the same line. The texts have to be glued :
Fichier numéro 12.Fichier numéro 13.

This is the last line of file number 1. It has to be glued to the first line of file 6.
And this is the first (and unique) line of the file number 6.

\chapter{Second chapter}
%
This is file number 4. The specificity is that it starts with a comment.


Le fichier numéro 7.


This is a txt file. Only for testing the "extension guessing" system.
   %
This is file number 9.

We are testing comments removal. 

Here is a line that as a percent as real comment : end of line here%

In the following, there should be one A and then one percent in huge size and the remaining line in normal size. (and of course this has to be normal size)

\huge

A\% 





\end{document}

%
